THESIS PROJECT PROPOSAL

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
matter (fermions) particles.The first generation of fermions consists of up (u) quark, down (d) quark, electron and electron 
neutrino,second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third generation of matter 
particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva,Switzerland.

@@

The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators 
like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The 
first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of 
these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified. In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.

>>>>

The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
matter (fermions) particles.The first generation of fermions consists of up (u) quark, down (d) quark, electron and electron 
neutrino,second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third generation of matter 
particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.

@@

The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators 
like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The 
first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of 
these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified. In the effective beyond standard model 
theory, there are dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and 
dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
